resistanceModelNotesAndy

### 2015-07-31 resistanceModelNotesAndy.Rmd
notes

@@

1. what is xerror in tree$cptable it seems to be not constant between analyses ??? It is the cross validation parameter.

1. compare sequence/mixture tree with 0/1 for 1 of the chosen trees

1. is using the optimal error the way that susannah has suggested a problem ?

>>>>

** 31/7/15 **
give more sensible error than "need finite 'xlim' values" from shiny curtis fig2 app
set starting freq of resistance to 0.0001 for each to generate the error.

this is when resistance is not reached within max generations.

runcurtis_f2()
plotcurtis_f2_generic()
Error in 1:ddt_cutoff : result would be too long a vector

@@

1. give more sensible error than "need finite 'xlim' values" from shiny curtis fig2 app
